---
title: "PDF document conversion 1"
subtitle: "your subtitle"
number-sections: true
# format: docx
format: pdf
fontsize: 12pt
mainfont: Times New Roman
sansfont: Times New Roman
pdf-engine: xelatex
bibliography: BibListReferences.bib
link-citations: true
csl: https://www.zotero.org/styles/apa
urlcolor: orange
linkcolor: blue
execute:
  echo: true
  warning: false
  message: false
---

This document uses:

- Custom font size

- Custom font

The YAML header can be configured as shown below.

This document uses a custom font size of 12 pt. Remove (or suppress) the \textcolor{Green}{fontsize: 12pt} from the YAML header to use the default font size settings.

We also specify **\textcolor{Red}{pdf-engine: xelatex}** as this engine is faster than *lualatex* for document conversion.

```{yaml}
---
fontsize: 12pt
mainfont: Times New Roman
sansfont: Times New Roman
pdf-engine: xelatex
---
```

\newpage

# Prep

```{r}
#| message: false
#| warning: false
library(tidyverse)
```

# Figure references

See @fig-1.

```{r}
#| label: fig-1
#| fig-cap: "Histogram of speed"

# hist(mtcars$wt)
 
ggplot(mtcars, aes(x = wt)) +   geom_histogram(binwidth = 0.3)
```

# Bib file

To obtain a bib file, you need to install Better BibTex that bridges **Zotero** and **markdown.** Visit here: <https://retorque.re/zotero-better-bibtex/>.

# Add references

<!-- left off, todo: figure out quarto referencing!! -->

Present your argument. This can be found in earlier studies [see @Anscombe1973, p.2; @Kabacoff2015].

@Kabacoff2015 [p.20] argues that...

\newpage

## Exercise 1 {.unnumbered}
Examine the rendered PDF document. 
- How do you apply font colour to text in a QMD document?
- How do you control both bold formatting and font colour for text in a QMD document?

# References {.unnumbered}
