---
title: "PDF document conversion 2"
subtitle: "your subtitle"
number-sections: true
# format: docx
format:
  pdf:
    toc: true
    toc-title: Contents
    include-in-header: 
      text: |
        \usepackage{dcolumn}
        \usepackage{fancyhdr}
        \pagestyle{fancy}
        \fancyhead[L]{Practical 6A}
        \fancyhead[C]{DASS}
        \fancyhead[R]{Section 6}
        \fancyfoot[C]{\thepage}
mainfont: Times New Roman
sansfont: Times New Roman
pdf-engine: xelatex    
bibliography: BibListReferences.bib
link-citations: true
csl: apa.csl
urlcolor: orange
linkcolor: blue
execute:
  echo: true
  warning: false
  message: false
---

\thispagestyle{empty}
\newpage
\setcounter{page}{1}

<!-- The option, `\setcounter{page}{1}` indicates that the title page is not counted in the pagination.  -->

This document uses:

- TOC titled *Contents*

- a front cover, and pagination begins on the second page.

- *include-in-header:* options in YAML to customise the header.

- Custom font


The YAML header can be configured as shown below. 

```{json}
---
number-sections: true
format:
  pdf:
    toc: true
    include-in-header: 
      text: |
        \usepackage{dcolumn}
        \usepackage{fancyhdr}
        \pagestyle{fancy}
        \fancyhead[L]{Practical 6A}
        \fancyhead[C]{DASS}
        \fancyhead[R]{Section 6}
        \fancyfoot[C]{\thepage}
---
```

**Technical tips**
Quarto uses KOMA-Script classes (scrartcl by default) and KOMA-Script suggests using scrlayer-scrpage latex package for handling header and footers instead of `fancyhdr` .

See here:
<https://stackoverflow.com/questions/75132359/header-and-footer-in-quarto-qmd-to-pdf>

Also, the official quarto manual: 
<https://quarto.org/docs/reference/formats/pdf.html>

```{r}
#| label: "setup"
#| include: FALSE
knitr::opts_chunk$set(echo = TRUE,  eval = TRUE)
```


# Prep

```{r}
#| message: false
#| warning: false
library(tidyverse)
```

# Figure references

See @fig-1.

```{r}
#| label: fig-1
#| fig-cap: "Histogram of speed"

# hist(mtcars$wt)
 
ggplot(mtcars, aes(x = wt)) +   geom_histogram(binwidth = 0.3)
```

# Bib file

To obtain a bib file, you need to install Better BibTex that bridges **Zotero** and **markdown.** Visit here: <https://retorque.re/zotero-better-bibtex/>.

# Add references

<!-- left off, todo: figure out quarto referencing!! -->

Present your argument. This can be found in earlier studies [see @Anscombe1973, p.2; @Kabacoff2015].

@Kabacoff2015 [p.20] argues that...


## Exercise 1 {.unnumbered}
Suppress the code from being displayed for Figure 1.
Use the `echo` option in the R code chunk.

## Exercise 2 {.unnumbered}
Customise your header.

## Exercise 3 {.unnumbered}
Practise adding a graph, using in-text referencing, and citing the relevant literature.

## Exercise 4 {.unnumbered}
What additional improvements can you make to enhance the appearance of the current PDF document? Implement the changes by experimenting with several design options. Recall the official quarto manual: 
<https://quarto.org/docs/reference/formats/pdf.html>

\newpage

# References {.unnumbered}


