---
title: "2.2 Figure titles"
author: "9622876"
output:
  bookdown::word_document2: 
    # toc: true
    fig_caption: yes
    number_sections: true
    global_numbering: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Figure references

See Figure \@ref(fig:speed).

```{r speed, fig.cap="Histogram of speed"}
hist(cars$speed)
```

\newpage

See Figure \@ref(fig:dist).

Dist indicates stopping distance (ft).

```{r dist, echo=FALSE, fig.cap="Histogram of dist"}
hist(cars$dist)
```

Note that the `echo = FALSE` suppresses the printing of the code, `hist(cars$dist)`.

\newpage

# Caveats
The figure name in the code chunk option can be sensitive! 
Experiment with names containing characters and numbers. For example, try with `hist-mpg2`.

See Figure \@ref(fig:hist-mpg2).

Does the figure number and title display correctly?
```{r hist-mpg2, fig.cap="Boxplot of mpg"}
boxplot(mtcars$mpg)
```


\newpage 

See Figure \@ref(fig:hist_mpg2).

Note that an underscore causes an error. Do not use use underscore as in `hist_mpg` as an figure ID.
```{r hist_mpg, fig.cap="Histogram of mpg"}
hist(mtcars$mpg)
```

# Comments in Rmarkdown 
Comments in Rmarkdown are indicated by `<!-- comments -->`.
<!-- Note that the `echo = FALSE` suppresses the printing of the code, `hist(cars$dist)`. -->

# Your task
Experiment with various code chunk options. What else can you improve with the resulting converted document?

# Reference

To learn cross-referencing for Tables, see <https://bookdown.org/yihui/rmarkdown-cookbook/cross-ref.html>
