---
title: "2.2 Bibliography and template"
author: "9622876"
output:
  bookdown::word_document2: 
    # toc: true
    fig_caption: yes
    number_sections: true
    global_numbering: true
    reference_docx: example_template.docx

bibliography: BibListReferences.bib
link-citations: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Add references

Present your argument. This can be found in earlier studies [see @Anscombe1973, p.2; @Kabacoff2015].

@Kabacoff2015 [p.20] argues that...

**Use square brackets and add a citation key following \@ symbol.** You may indicate page numbers following the citation key. *Please note that these in-text citations need to be sorted!*

# Bib file

To obtain a bib file, you need to install **Better BibTex** that bridges Zotero and markdown. Visit here: <https://retorque.re/zotero-better-bibtex/>. You can download the latest version here: <https://github.com/retorquere/zotero-better-bibtex/releases>. Choose .xpi file only (you do not need other files). As the whole procedure can be involved, it would be sensible to consider ways to revisit it at a later stage!

\newpage

# Data visualisation

See Figure \@ref(fig:speed).

```{r speed, fig.cap="Histogram of speed"}
hist(cars$speed)
```

# Creating a Word template

We use the converted docx document, `2.3_Rmd_Bib_WordTemplate.docx` as a template.

To do so, we save `2.3_Rmd_Bib_WordTemplate.docx`  as `custom_template.docx`.

We are now ready to customise this template file.

## Customising heading

Open `custom_template.docx` and apply your own format to Heading 1. 

To customize, we use `Styles` in Word menu.

- First, place the cursor in any Heading 1. 
- Then, access **Styles tab** 
- You will see **Heading 1** is selected. 
- Reveal **Modify** menu (in Windows: simply right-click, in Mac: press Control and click *Heading 1*)
- Apply your own formatting (e.g. font size)

Do the same with other Styles. Do not forget to include page numbers!

## Your task: customising Function Tok

- Click on *hist* under *3 Data visualisation*. Currently, `FunctionTok` is displayed in dark blue. 
- In Word, go to Styles and locate `FunctionTok` before accessing *Modify* menu. 
- Customise the `FunctionTok` Style by applying a different colour of your choice.

## Your task
Verify the Style of **$** symbol used in the following code.

> `hist(cars$speed)`

What is this particular style called? Customise other *Styles* to your liking. 

## Using a custom Word template in an Rmd file
When you are satisfied with the new template, we will specify this new template in a new Rmd file. In the YAML header at the top, declare the template as `reference_docx:custom_template.docx`.

# References
