---
title: "2.2 Bibliography and template"
author: "9622876"
output:
  bookdown::word_document2: 
    # toc: true
    fig_caption: yes
    number_sections: true
    global_numbering: true
    reference_docx: example_custom_template.docx

bibliography: BibListReferences.bib
link-citations: true
---

   
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Add references

Present your argument. This can be found in earlier studies [see @Anscombe1973, p.2; @Kabacoff2015]. 

@Kabacoff2015 [p.20] argues that... 

**Use square brackets and add a citation key following @ symbol.** You may indicate page numbers following the citation key. *Please note that these in-text citations needs to be sorted!*

# Bib file
To obtain a bib file, you need to install Better BibTex that bridges Zotero and markdown. Visit here:
<https://retorque.re/zotero-better-bibtex/>.
You can download the latest version here: <https://github.com/retorquere/zotero-better-bibtex/releases>. Choose .xpi file only (you do not need other files). As the whole procedure can be involved, it would be sensible to consider ways to revisit it at a later stage!

\newpage

# Data visualisation

See Figure \@ref(fig:speed).

```{r speed, fig.cap="Histogram of speed"}
hist(cars$speed)
```


\newpage

Figure \@ref(fig:dist) illustrates...

```{r dist, echo=FALSE, fig.cap="Histogram of dist"}
hist(cars$dist)
```

#  Styles and formatting 
We use the converted docx document, `2.3_Rmd_Bib_WordTemplate.docx` as a template. 

To do so, we rename `2.3_Rmd_Bib_WordTemplate.docx` and save as `custom_template.docx`. 

We are now ready to customise this template file. 

Open `custom_template.docx` and apply your own format to Heading 1. Place the cursor in any Heading 1. In Word, access **Styles tab** and choose **Heading 1** Modify as appropriate. Do not forget to include page numbers!

When you are satisfied with the new template, we will specify this new template in the YAML header at the top as `reference_docx:custom_template.docx`.


# References