---
title: "3.1 First PDF conversion"
author: "9522221"
output:
  pdf_document:
    toc: true
fontsize: 12pt
urlcolor: blue
linkcolor: orange
---

\thispagestyle{empty}

\newpage

\setcounter{page}{1}


# Add references

Present your argument. This can be found in earlier studies [see @Anscombe1973, p.2; @Kabacoff2015]. 

@Kabacoff2015 [p.20] argues that... 

**Use square brackets and add a citation key following @ symbol.** You may indicate page numbers following the citation key. *Please note that these in-text citations needs to be sorted!*

# Bib file
To obtain a bib file, you need to install Better BibTex that bridges Zotero and markdown. Visit here:
<https://retorque.re/zotero-better-bibtex/>.
You can download the latest version here: <https://github.com/retorquere/zotero-better-bibtex/releases>. Choose .xpi file only (you do not need other files). As the whole procedure can be involved, it would be sensible to consider ways to revisit it at a later stage!

\newpage

# Data visualisation

See Figure \@ref(fig:speed).

```{r speed, fig.cap="Histogram of speed"}
hist(cars$speed)
```


\newpage

Figure \@ref(fig:dist) illustrates...

```{r dist, echo=FALSE, fig.cap="Histogram of dist"}
hist(cars$dist)
```

# References