---
title: "3.2 Using fancyhdr and custom fonts"
author: "98555521"
mainfont: Times New Roman
output:
  bookdown::pdf_document2:
    toc: true
    df_print: kable
    highlight: haddock
    number_sections: true
    latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
linkcolor: orange
header-includes:
- \usepackage{dcolumn}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[L]{Practical 4A}
- \fancyhead[C]{DASS}
- \fancyhead[R]{Section 4}
- \fancyfoot[C]{\thepage}
---
---
title: "3.1 First PDF conversion"
author: "9522221"
output:
  pdf_document:
    toc: true
fontsize: 10pt
urlcolor: blue
linkcolor: orange
---

\thispagestyle{empty}

\newpage

\setcounter{page}{1}

<!-- The option, `\setcounter{page}{1}` indicates that the title page is not counted in the pagination.  -->

<!-- https://ctan.org/pkg/fancyhdr?lang=en-->

\newpage

# Using a custom font
We need to specify xelatex as latex_engine.

Set the font, and specify xelatex as latex_engine.

```
mainfont: Times New Roman
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
```

\newpage

# Data visualisation

See Figure \@ref(fig:speed).

```{r speed, fig.cap="Histogram of speed"}
hist(cars$speed)
```


\newpage

Figure \@ref(fig:dist) illustrates...

```{r dist, echo=FALSE, fig.cap="Histogram of dist"}
hist(cars$dist)
```
