---
title: "RMarkdown to PDF using stargazer"
author: "5895464"
output:
  bookdown::pdf_document2:
    df_print: kable
    highlight: haddock
    number_sections: true
    latex_engine: xelatex
  word_document: default
fontsize: 10pt
urlcolor: blue
linkcolor: orange
header-includes:
- \usepackage{dcolumn}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[C]{DASS}
- \fancyhead[L]{Practical 4A}
- \fancyhead[R]{Section 4}
- \fancyfoot[C]{\thepage}
bibliography: BibListReferences.bib
link-citations: true
---

\thispagestyle{empty}

\newpage

\setcounter{page}{1}


# Introduction

Referencing examples:

Present your argument. This can be found in earlier studies [see @Anscombe1973, p.2; @Kabacoff2015]. @Kabacoff2015 [p.20] argues that..

```{r, echo = FALSE, message = FALSE}
library(stargazer)
```


```{r cars}
model_A <- lm(dist ~ speed, data = cars)
```


```{r, results = 'asis'}
stargazer(model_A, type = "latex", title = "Model Results", align = TRUE, header = FALSE)
```

\newpage 

# Including Plots

You can also embed plots, for example:

```{r pressure, fig.cap = "Pressure Plot", fig.align = "center", fig.height = 4, fig.width = 5}
plot(pressure ~ temperature, data = pressure)
```

Note: This is a scatterplot illustrating the vapor pressure of Mercury as a Function of Temperature, which is based on R's built-in dataset, `pressure`. 

\newpage 

Here's a quick glance of the *pressure* dataset.

```{r scatterp, echo = FALSE}
knitr::kable(head(pressure), caption = "Pressure data")
```

# Your task
Add cross-referencing for the Figures and Tables above.

\newpage 

# References