---
title: "Rmarkdown with a custom template"
author: "9622876"
date: "September 17th, 2024"
output:
  bookdown::word_document2: 
    # toc: true
    fig_caption: yes
    number_sections: true
    global_numbering: true
    reference_docx: example_custom_template.docx

bibliography: BibListReferences.bib
link-citations: true
---

   
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#  Styles and formatting 
Save the converted docx document, `Rmd_test2.docx` as `custom_template.docx`. 
We open `custom_template.docx` and use as a Word template. 

Place the cursor in any Heading 1. In Word, access **Styles tab** and choose **Heading 1** Modify as appropriate. Don't forget to include page numbers!
Then, in Rmd_test3.Rmd, we will modify YAML.
Specify at the top as `reference_docx:custom_template.docx`.

\newpage

# Data visualisation

See Figure \@ref(fig:speed).

```{r speed, fig.cap="Histogram of speed"}
hist(cars$speed)
```


\newpage

Figure \@ref(fig:dist) illustrates...

```{r dist, echo=FALSE, fig.cap="Histogram of dist"}
hist(cars$dist)
```

Well-done! ðŸ‘ 

# Your turn

Create a blank Rmd file.

How do you create this Rmarkdown file?

In RStudio, go to File \> New file \> R Markdown... When a new window pops up, choose Word as Default Output Format. Click OK.

The default Rmarkdown file looks complex. Delete the text as necessary. Explore the file.

Experiment with Rmd. Convert to HTML, Word, and PDF. Improve the look by tweaking further. Learn code chunk options.


# Add references

Present your argument. This can be found in earlier studies [see @Anscombe1973, p.2; @Kabacoff2015]. 

@Kabacoff2015 [p.20] argues that... 

**Use square brackets and add a citation key following @ symbol.** You may indicate page numbers following the citation key. *Please note that these in-text citations needs to be sorted!*

To obtain a bib file, you need to install Better BibTex that bridges Zotero and markdown. Visit here:
<https://retorque.re/zotero-better-bibtex/>.
You can download the latest version here: <https://github.com/retorquere/zotero-better-bibtex/releases>. Choose .xpi file only (you do not need other files). As the whole procedure can be involved, it would be sensible to consider ways to revisit it at a later stage!


# References