---
title: "Rmarkdown with a custom template"
author: "9622876"
date: "September 17th, 2024"
output:
  bookdown::word_document2: 
    # toc: true
    fig_caption: yes
    number_sections: true
    global_numbering: true
    reference_docx: example_custom_template.docx
---

   
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#  Styles and formatting 
Save the converted docx document, `Rmd_test2.docx` as `custom_template.docx`. 
We open `custom_template.docx` and use as a Word template. 

In Word, access Styles tab and choose Heading. Modify as appropriate. Don't forget to include page numbers!
Then, in Rmd_test3.Rmd, we will modify YAML.
Specify at the top as `reference_docx:custom_template.docx`.


\newpage

# Data visualisation

See Figure \@ref(fig:speed).


```{r speed, fig.cap="Histogram of speed"}
hist(cars$speed)
```


\newpage

Figure \@ref(fig:dist) illustrates...

```{r dist, echo=FALSE, fig.cap="Histogram of dist"}
hist(cars$dist)
```

Well-done! ðŸ‘ 

# Your turn

Create a blank Rmd file.

How do you create this Rmarkdown file?

In RStudio, go to File \> New file \> R Markdown... When a new window pops up, choose Word as Default Output Format. Click OK.

The default Rmarkdown file looks complex. Delete the text as necessary. Explore the file.

Experiment with Rmd. Convert to HTML, Word, and PDF. Improve the look by tweaking further. Learn code chunk options.
