---
title: "Code export to Word"
output:
  word_document:
    number_sections: yes
    reference_docx: 0_Template_Code_export.docx
---

Here's a brief tutorial. To export R code to Word, we can use Rmarkdown. Don't worry, we only use a very simple Rmarkdown file. 

Where does the code go? R Code will be placed under ```{r}. This means R code is enclosed in the curly brackets. We do not need the output such as tables and figures, but just the code. So, we specify eval=FALSE.

This means that you do not actually run the code, but simply PRINT the code. 

Put your R code in the blank (line 25). Save. Then, click on Knit (the incon looks similar to 🧵 ).

The icon resembles a needle and thread as Knit implies. It is placed with other menu icons at the top, just under the filename. Alternatively, you can press Ctrl+Shift+P (or Cmd+Shift+P in Mac), then type Knit, before pressing Enter. If you have an opened (code-exported) word document already, ensure to close it before you Knit. I hope it works!

Once R launches the exported Word document, you can copy the code in the grey box to the Appendix of your report. Make sure this step works correctly. Test it several times to get it right! Good luck!

Example:
```{r, eval= FALSE}
library("tableone")   # Desc stats
library("janitor")    # Cross-tabs, tabyl()

## > Step 1: Read and inspect the data ----
temp <- read_csv("simd_cleaned.csv")
```

Your code:
```{r, eval= FALSE}



```

# How do you create this Rmarkdown file?

To create a Rmarkdown file, in RStudio, go to File > New file > R Markdown...
When a new window pops up, choose Word as Default Output Format. Click OK.

The default Rmarkdown file looks more complex than this. Explore the file as necessary.

# Customising template:

Currently, comments are in brown. To customize, we use Styles in Word menu.
Click on *Desc* behind # symbol. In Word, go to Styles and click on ⇲ con placed at the right-corner. You’ll see the Style, CommentTok is applied. 
Modify the CommentTok Style by applying a different colour of your choice.
