---
title: "Rmarkdown prac"
output:
  word_document:
    number_sections: yes
    reference_docx: 0_Template_Code_export.docx
---

# Embedding R code

We press **Ctrl (Cmd) + Alt + I**.

```{r}

```

```{r}

```

```{r}
data(mtcars)
head(mtcars)
```

Does it amaze you? Well, using rmarkdown is much more complex than the above example! Your data analysis steps involve multiple stages and you'll be selective in presenting results.

In practice, you'll run the entire file first then load the objects before printing. This is an example only, and the output will not be printed.

Example:
```{r}
source("P:/SRMS-Workshop/R-Source-Scripts/Code_to_test1.R") # Specify the full path for an R script
```

Testing yours: 
```{r}
# source("yourpath/filename.R") # Specify the full path for an R script
```

As an R script is run, we now have access to objects (Tables, and Figures) we need to present in a report. Let's imagine that we are presenting a Figure on car speed.
```{r}
# Figure
p1_carspeed

# Desc stats (specify obj name)
# descstats
```

#  Styles and formatting 
Use a Word template. Go to Styles tab and choose Heading. Modify as appropriate. Specify at the top as reference_docx:yourtemplate.docx.

Also see BB for tutorial on Styles. 

# To create a Word document using the current Rmd file
Click on Knit (the icon looks similar to 🧶).

The icon resembles a needle and thread as Knit implies. It is placed with other menu icons at the top, just under the filename.

Alternatively, you can press Ctrl+Shift+K (or Cmd+Shift+ in Mac)

If you have an opened (code-exported) word document already, ensure to close it before you Knit. I hope it works!

Well-done! 👍
